Reply To Examiners

### 2014-05-19 answer_thesis_examiner/chap3.tex
auto

\replyToComment
    {
      A thesis is supposed to persuade others to believe what you have proposed and to use it.
      How can you expect others to believe in you, when you don't know what most of what it is supposed to do?
    }
    {
      The methodology that is employed to persuade people into believing the proposed models is to follow rigorious mathematical transformations coupled with experiments.
      The thesis also includes a chapter detailing multiple different applications of the proposed models.
      What else the proposed models can applied on, I feel, is a totally different matter.
      In the end, Eistein probably did not forsee that his theory were used to create atomic bombs and killed thousands of people!
    }

@@

While the conference papers have been published and the journal paper submitted,
  their copies have been removed from this section.

>>>>

\replyToComment
    {
      A thesis is supposed to persuade others to believe what you have proposed and to use it.
      How can you expect others to believe in you, when you don't know what most of what it is supposed to do?
    }
    {
     To persuade people into believing its proposed models, the thesis follows rigorous scientific methodologies. 
     They include theoretical mathematics transformations and realistic hypothesis-testing experiments.
      The thesis also includes a chapter detailing several different applications of the proposed models.
      These applications, due to the various practical constraint, are unlikely to be exhaustive over all future applications.

In fact, the two topics of 1) what else the proposed models can be applied on and 2) if the proposed models are to be taken as true, I feel, are not much related.
      In the end, Einstein probably did not foresee that his theories were used to create atomic bombs and killed thousands of people.
This lack of foresight however does not cast any doubt on his contribution to our scientific progress.
    }

@@

\replyToComment
    {It is not ususal to attach copies of academic papers in the Appendix.}
    {The attached papers were removed from the Appendix.}

%While the conference papers have been published and the journal paper submitted,
%  their copies have been removed from this section.
